Engineering the Servo Web Browser Engine using Rust

### 2015-10-23 icse16-servo/paper.tex
New code count numbers. Talk more about the soft. eng. bits
Enable sloppy
vgosu's comments

\documentclass[preprint]{../common/acm_proc_article-sp}

@@

\author{
\alignauthor
Brian Anderson\\
       \affaddr{Mozilla Research}\\
       \email{banderson@mozilla.com}
\alignauthor
Lars Bergstrom\\
       \affaddr{Mozilla Research}\\
       \email{larsberg@mozilla.com}
\alignauthor
Manish Goregaokar\\
       \affaddr{Indian Institute of Technology Bombay}\\
       \email{manishg@iitb.ac.in}
\and
\alignauthor
Josh Matthews\\
       \affaddr{Mozilla}\\
       \email{jdm@mozilla.com}
\alignauthor
Keegan McAllister\titlenote{Work performed while employed at Mozilla}\\
       \email{mcallister.keegan@gmail.com}
\alignauthor
Jack Moffitt\\
       \affaddr{Mozilla}\\
       \email{jack@mozilla.com}
\and
\alignauthor
Simon Sapin\\
       \affaddr{Mozilla}\\
       \email{ssapin@mozilla.com}
}

@@

%\sloppy

@@

We would like to thank Robert Clipsham, David Herman, Tim Kuehn, Lindsey Kuper,
Ms2ger, and Ben Striegel for their comments on drafts of this paper.

>>>>

\documentclass[preprint]{../common/sig-alternate}

@@

\author{
\alignauthor
Brian Anderson\\
       \affaddr{Mozilla Research}\\
       \email{banderson@mozilla.com}
\alignauthor
Lars Bergstrom\\
       \affaddr{Mozilla Research}\\
       \email{larsberg@mozilla.com}
\alignauthor
Manish Goregaokar\\
       \affaddr{Indian Institute of Technology Bombay}\\
       \email{manishg@iitb.ac.in}
\and
\alignauthor
Josh Matthews\\
       \affaddr{Mozilla Research}\\
       \email{jdm@mozilla.com}
\alignauthor
Keegan McAllister\titlenote{Work performed while employed at Mozilla}\\
       \email{mcallister.keegan@gmail.com}
\alignauthor
Jack Moffitt\\
       \affaddr{Mozilla Research}\\
       \email{jack@mozilla.com}
\and
\alignauthor
Simon Sapin\\
       \affaddr{Mozilla Research}\\
       \email{ssapin@mozilla.com}
}

@@

\sloppy

@@

We would like to thank Robert Clipsham, Valentin Gosu, David Herman, Tim Kuehn,
Lindsey Kuper, Ms2ger, and Ben Striegel for their comments on drafts of this paper.

### 2015-10-23 icse16-servo/servo.tex
vgosu's comments

\subsection{Rust's syntax}
Rust has struct and enum types (similar to Standard ML's record types and datatypes~\cite{sml97-definition}) as
well as pattern matching.
These types and associated language features provide two large benefits to Servo over traditional browsers
written in \Cplusplus{}.
First, creating new abstractions and intermediate representations is syntactically easy, so there is very little
pressure to tack additional fields into classes simply to avoid creating a large number of new header and implementation
files.
More importantly, pattern matching with static dispatch is typically faster than a virtual function call on a class
hierarchy.
Virtual functions can both have an in-memory storage cost associated with the virtual function tables (sometimes many thousands of bytes\footnote{\url{https://chromium.googlesource.com/chromium/blink/+/c048c5c7c2578274d82faf96e9ebda4c55e428da}}) but more importantly
incur indirect function call costs.
All \Cplusplus{} browser implementations transform performance-critical code to either use the \lstinline[language=C]{final}
specifier wherever possible or specialize the code in some other way to avoid this cost.

@@

In the future, we hope to expose our Rust libraries written for Servo to C, in order to reuse them
in the Firefox web brower.
A first potential libraries is our Rust-based URL parser.\footnote{https://github.com/servo/rust-url}
While URL parsing seems like a simple and secure task, an audit of the public security bugs\footnote{Firefox public security bugs: http://mzl.la/1GkOiIC} shows that all four of the ones that come from URL parsing are related to either indexing out of
range of a raw memory buffer or using data that had already been freed --- both of which are
prevented by Rust code.

>>>>

\subsection{Rust's syntax}
Rust has struct and enum types (similar to Standard ML's record types and datatypes~\cite{sml97-definition}) as
well as pattern matching.
These types and associated language features provide two large benefits to Servo over traditional browsers
written in \Cplusplus{}.
First, creating new abstractions and intermediate representations is syntactically easy, so there is very little
pressure to tack additional fields into classes simply to avoid creating a large number of new header and implementation
files.
More importantly, pattern matching with static dispatch is typically faster than a virtual function call on a class
hierarchy.
Virtual functions can have an in-memory storage cost associated with the virtual function tables (sometimes many thousands of bytes\footnote{\url{https://chromium.googlesource.com/chromium/blink/+/c048c5c7c2578274d82faf96e9ebda4c55e428da}}) but more importantly
incur indirect function call costs.
All \Cplusplus{} browser implementations transform performance-critical code to either use the \lstinline[language=C]{final}
specifier wherever possible or specialize the code in some other way to avoid this cost.

@@

In the future, we hope to expose our Rust libraries written for Servo to C, in order to reuse them
in the Firefox web brower.
A first potential library is our Rust-based URL parser.\footnote{https://github.com/servo/rust-url}
While URL parsing seems like a simple and secure task, an audit of the public security bugs\footnote{Firefox public security bugs: http://mzl.la/1GkOiIC} shows that all four of the ones that come from URL parsing are related to either indexing out of
range of a raw memory buffer or using data that had already been freed --- both of which are
prevented by Rust code.
